Classless Java: Tuning Java Interfaces

### 2015-12-02 paper/sections/Appendix.tex
Proof in the appendix, fixed and added notes.

\textbf{LEMMA 1. }
For any expression $e$ under an interface table $\II_0\ldots\II_n$ with $\Gamma\vdash e\in\C$, if $\II_0$ has \textbf{@ObjWeak} and $[\![\II_0]\!]$ is well-defined, then under the interface table $[\![\II_0]\!]\II_1\ldots\II_n$, $\Gamma\vdash e\in\_<:\C$.
\begin{proof}
The proof is based on induction. By the grammar shown in Figure~\ref{Grammar}, there are three cases for an arbitrary expression $e$:
\begin{itemize}
\item A variable or a field update. The type preservation for $e$ is ensured by induction.
\item A method call (normal, static or super). Such a method won't be ``removed'' by the translation and is still there, and the types remain unchanged. The only work \textbf{@ObjWeak} does is adding a static method $\QM{of}$ to the interface, however, a pre-condition of the translation is $\QM{of}\notin\dom(\C_0)$, so adding $\QM{of}$ method has no way to affect any method call.
\item An object creation. Adding the $\QM{of}$ method doesn't introduce unimplemented methods to an interface, moreover, the static method is not inheritable, hence after translation such an object creation still type checks and has the right type by induction.
\end{itemize}
\end{proof}

@@

\textbf{LEMMA 2. }
If $\II_0$ has \textbf{@ObjWeak} and is OK, then $[\![\II_0]\!]$ OK.
\begin{proof}

@@

\begin{itemize}
\item All field initializations are type correct. By the definition of $\ofMethod(\C_0)$ in Section~\ref{subsec:ofmethod}, the fields $m_1,\ldots,m_n$ are initialized by $\QM{of}$'s arguments, and types are compatible.
\item All method bodies are well-typed.
    \begin{itemize}
    \item Typing of the $i$-th getter $m_i$. \[\Gamma, m_i:\C_i, \QM{this}:\C_0 \vdash m_i\in \C_i\]
        We know that $\C_i=\C^{\mh_i}$ since the $i$-th getter has its return type the same as the corresponding field $m_i$.
    \item Typing of the \QM{with-} method of an arbitrary field $m_i$. By Section~\ref{subsec:ofmethod}, if the \QM{with-} method of $m_i$ is well-defined, it has the form \[\C_0\ \QM{with#}\m_i\oR \C_i\ \QM{_val}\cR\ \QM{\{}\QM{return}\ \C_0\QM{.of(}\es_i\QM{);\}}\]
        $\es_i$ is obtained by replacing $m_i$ with $\QM{_val}$ in the list of fields, and since they have the same type $\C_i$, the arguments $\es_i$ are compatible with $\C_0.\QM{of}$ method. Hence \[\Gamma, \overline{m_i:\C_i}, \QM{this}:\C_0,\ \QM{_val} : \C_i \vdash \C_0\QM{.of}\oR\es_i\cR\in \C_0\]
        We know that $\C_0=\C^{\mh_i}$ by the return type of $\QM{with#}\m_i$ shown as above.
    \item Typing of the $i$-th setter \QM_$m_i$. If the \QM_$m_i$ method is well-defined, it has the form
        \[\C_0\ \QM_\m_i\oR \C_i\ \QM{_val}\cR\ \QM{\{} \m_i\QM{= _val;return this;\}}\]
        By \rn{t-Update}, the assignment ``$\m_i\QM{= _val;}$'' is correct since $\m_i$ and $\QM{_val}$ have the same type $I_i$, and the return type is decided by \QM{this}. \[\Gamma, \QM{this}:\C_0,\ \QM{_val} : \C_i \vdash\QM{this}\in \C_0\]
        We know that $\C_0=\C^{\mh_i}$ by the return type of $\QM_\m_i$ shown as above.\\
        \haoyuan{Can we write $\Gamma, \QM{this}:\C_0,\ \QM{_val} : \C_i, \C^{\mh_i} = \C_0 \vdash\QM{this}\in \C_0 = \C^{\mh_i}$?}\\
        \haoyuan{Can we write $\QM{\{} \m_i\QM{= _val;return this;\}} \in \C_0$?}
    \end{itemize}
\item All method headers are valid with respect to the domain of $\C_0$. Namely $$\sigvalid(\mh_1\ldots\mh_n,I)$$
    \begin{itemize}
    \item For the $i$-th getter $m_i$,
        \begin{align*}
        &\C_i\ \m_i\oR\cR\ \QM{\{...\}}\in\ofMethod(\C_0)\\
        \mimply\hspace{.2in}& \C_i\ \m_i\oR\cR\QM; \in \fieldsFunc(\C_0)\\
        \mimply\hspace{.2in}& \C_i\ \m_i\oR\cR\QM; = \mBody(m_i,\C_0)\\
        \mimply\hspace{.2in}& \C_i\ \m_i\oR\cR\QM; <: \mBody(m_i,\C_0)
        \end{align*}
    \item For the $\QM{with#}\m_i$ method,
        \begin{align*}
        &\C_0\ \QM{with#}\m_i\oR \C_i\ \QM{_val}\cR\ \QM{\{...\}}\in\ofMethod(\C_0)\\
        \mimply\hspace{.2in}& \mBody(\QM{with#}\m_i,\C_0) \mbox{ is of form }\mh\QM;\\
        \mbox{with}\hspace{.2in}& \valid(\C_0)\\
        \mimply\hspace{.2in}& \isWith(\mBody(\QM{with#}\m_i,\C_0),\C_0)\\
        \mimply\hspace{.2in}& \C_0\ \QM{with#}\m_i\oR \C_i\ \QM{_val}\cR\QM; <: \mBody(\QM{with#}\m_i,\C_0)
        \end{align*}
    \item For the $i$-th setter $\QM_\m_i$,
        \begin{align*}
        &\C_0\ \QM_\m_i\oR \C_i\ \QM{_val}\cR\ \QM{\{...\}}\in\ofMethod(\C_0)\\
        \mimply\hspace{.2in}& \mBody(\QM_\m_i,\C_0) \mbox{ is of form }\mh\QM;\\
        \mbox{with}\hspace{.2in}& \valid(\C_0)\\
        \mimply\hspace{.2in}& \isSetter(\mBody(\QM_\m_i,\C_0),\C_0)\\
        \mimply\hspace{.2in}& \C_0\ \QM_\m_i\oR \C_i\ \QM{_val}\cR\QM; <: \mBody(\QM_\m_i,\C_0)
        \end{align*}
    \end{itemize}
\item All abstract methods in the domain of $\C_0$ have been implemented. Namely $$\alldefined(\mh_1\ldots\mh_n,I)$$
    Here we simply refer to $\valid(\C_0)$, since it guarantees each abstract method to satisfy $\isField$, $\isWith$ or $\isSetter$. But that object includes all implementations for those cases, hence it is of type $\C_0$ by \rn{t-Obj}.
\end{itemize}

@@

\subsection{Proof of THEOREM}\label{subsec:proof3}
\begin{proof}
\textbf{LEMMA 2} already proves that $[\![\II_0]\!]$ is OK. On the other hand, for any $\II\ne\II_0$, by \textbf{LEMMA 1}, we know that all its methods
are still well-typed, and the generated code in translation of \textbf{@ObjWeak} is only a static method \QM{of}, which has no way to affect the domain
of $\II$, so after translation rule \rn{t-Intf} can still be applied, which finishes our proof.
\end{proof}

>>>>

\textbf{LEMMA 1. }
For any expression $e$ under an interface table $\II_0\ldots\II_n$ with $\Gamma\vdash e\in\C$, if $\II_0$ has \textbf{@ObjWeak} and $[\![\II_0]\!]$ is well-defined, then under the interface table $[\![\II_0]\!]\II_1\ldots\II_n$, $\Gamma\vdash e\in\_<:\C$.
\begin{proof}
By induction on the typing rules: by the grammar shown in Figure~\ref{Grammar}, there are 6 cases for an arbitrary expression $e$:
\begin{itemize}
\item Variables are typed in the same exact way.
\item Field update. The type preservation is ensured by induction.
\item A method call (normal, static or super). The corresponding method declaration won't be ``removed'' by the translation, also the types remain unchanged. The only work \textbf{@ObjWeak} does is adding a static method $\QM{of}$ to the interface, however, a pre-condition of the translation is $\QM{of}\notin\dom(\C_0)$, so adding $\QM{of}$ method has no way to affect any formerly well typed method call.
\item An object creation. Adding the $\QM{of}$ method doesn't introduce unimplemented methods to an interface, moreover, the static method is not inheritable, hence after translation such an object creation still type checks and has the right type by induction.
\end{itemize}
\end{proof}

@@

\textbf{LEMMA 2. }
If $\II_0$ has \textbf{@ObjWeak} and $\C_0$ OK, then $[\![\II_0]\!]$ OK.
\begin{proof}

@@

\begin{itemize}
\item All field initializations are type correct. By the definition of $\ofMethod(\C_0)$ in Section~\ref{subsec:ofmethod}, the fields $m_1,\ldots,m_n$ are initialized by $\QM{of}$'s arguments, and types are compatible.
\item All method bodies are well-typed.
    \begin{itemize}
    \item Typing of the $i$-th getter $m_i$. \[\Gamma, m_i:\C_i, \QM{this}:\C_0 \vdash m_i\in \C_i\]
        We know that $\C_i=\C^{\mh_i}$ since the $i$-th getter has its return type the same as the corresponding field $m_i$.
    \item Typing of the \QM{with-} method of an arbitrary field $m_i$. By Section~\ref{subsec:ofmethod}, if the \QM{with-} method of $m_i$ is well-defined, it has the form \[\C_0\ \QM{with#}\m_i\oR \C_i\ \QM{_val}\cR\ \QM{\{}\QM{return}\ \C_0\QM{.of(}\es_i\QM{);\}}\]
        $\es_i$ is obtained by replacing $m_i$ with $\QM{_val}$ in the list of fields, and since they have the same type $\C_i$, the arguments $\es_i$ are compatible with $\C_0.\QM{of}$ method. Hence \[\Gamma, m_1:\C_1\ldots m_n:\C_n, \QM{this}:\C_0,\ \QM{_val} : \C_i \vdash \C_0\QM{.of}\oR\es_i\cR\in \C_0\]
        We know that $\C_0=\C^{\mh_i}$ by the return type of $\QM{with#}\m_i$ shown as above.
    \item Typing of the $i$-th setter \QM_$m_i$. If the \QM_$m_i$ method is well-defined, it has the form
        \[\C_0\ \QM_\m_i\oR \C_i\ \QM{_val}\cR\ \QM{\{} \m_i\QM{= _val;return this;\}}\]
        By \rn{t-Update}, the assignment ``$\m_i\QM{= _val;}$'' is correct since $\m_i$ and $\QM{_val}$ have the same type $I_i$, and the return type is decided by \QM{this}. \[\Gamma, \QM{this}:\C_0,\ \QM{_val} : \C_i \vdash\QM{this}\in \C_0\]
        We know that $\C_0=\C^{\mh_i}$ by the return type of $\QM_\m_i$ shown as above.\\
        \haoyuan{Can we write $\Gamma, \QM{this}:\C_0,\ \QM{_val} : \C_i, \C^{\mh_i} = \C_0 \vdash\QM{this}\in \C_0 = \C^{\mh_i}$?}\\
        \haoyuan{Can we write $\QM{\{} \m_i\QM{= _val;return this;\}} \in \C_0$?}
      \marco{Not without defining what that would mean. Do we need to? it seams good as it is now...}
    \end{itemize}
\item All method headers are valid with respect to the domain of $\C_0$. Namely $$\sigvalid(\mh_1\ldots\mh_n,I)$$
    \begin{itemize}
    \item For the $i$-th getter $m_i$,
        \begin{align*}
        &\C_i\ \m_i\oR\cR\ \QM{\{...\}}\in\ofMethod(\C_0)\\
        \mimply\hspace{.2in}& \C_i\ \m_i\oR\cR\QM; \in \fieldsFunc(\C_0)\\
        \mimply\hspace{.2in}& \C_i\ \m_i\oR\cR\QM; = \mBody(m_i,\C_0)\\
        \mimply\hspace{.2in}& \C_i\ \m_i\oR\cR\QM; <: \mBody(m_i,\C_0)
        \end{align*}\marco{I do not understand this point, I think ofMethod is not what you want to write, but I can not understand what you want do do...}
    \item For the $\QM{with#}\m_i$ method,
        \begin{align*}
        &\C_0\ \QM{with#}\m_i\oR \C_i\ \QM{_val}\cR\ \QM{\{...\}}\in\ofMethod(\C_0)\\
        \mimply\hspace{.2in}& \mBody(\QM{with#}\m_i,\C_0) \mbox{ is of form }\mh\QM;\\
        \mbox{with}\hspace{.2in}& \valid(\C_0)\\
        \mimply\hspace{.2in}& \isWith(\mBody(\QM{with#}\m_i,\C_0),\C_0)\\
        \mimply\hspace{.2in}& \C_0\ \QM{with#}\m_i\oR \C_i\ \QM{_val}\cR\QM; <: \mBody(\QM{with#}\m_i,\C_0)
        \end{align*}
    \item For the $i$-th setter $\QM_\m_i$,
        \begin{align*}
        &\C_0\ \QM_\m_i\oR \C_i\ \QM{_val}\cR\ \QM{\{...\}}\in\ofMethod(\C_0)\\
        \mimply\hspace{.2in}& \mBody(\QM_\m_i,\C_0) \mbox{ is of form }\mh\QM;\\
        \mbox{with}\hspace{.2in}& \valid(\C_0)\\
        \mimply\hspace{.2in}& \isSetter(\mBody(\QM_\m_i,\C_0),\C_0)\\
        \mimply\hspace{.2in}& \C_0\ \QM_\m_i\oR \C_i\ \QM{_val}\cR\QM; <: \mBody(\QM_\m_i,\C_0)
        \end{align*}
    \end{itemize}
\item All abstract methods in the domain of $\C_0$ have been implemented. Namely $$\alldefined(\mh_1\ldots\mh_n,I)$$
    Here we simply refer to $\valid(\C_0)$, since it guarantees each abstract method to satisfy $\isField$, $\isWith$ or $\isSetter$. But that object includes all implementations for those cases\marco{you need to expand here, proof that we have all the implementations for all cases by using the definition of ofMethod}, hence it is of type $\C_0$ by \rn{t-Obj}.
\end{itemize}

@@

\subsection{Proof of THEOREM}
\marco{the therem statement must be here}
\label{subsec:proof3}
\begin{proof}
\textbf{LEMMA 2} already proves that $[\![\II_0]\!]$ is OK. On the other hand, for any $\II\ne\II_0$, by \textbf{LEMMA 1}, we know that all its methods
are still well-typed, and the generated code in translation of \textbf{@ObjWeak} is only a static method \QM{of}, which has no way to affect the domain
of $\II$, so after translation rule \rn{t-Intf} can still be applied, which finishes our proof.
\end{proof}

### 2015-12-02 paper/sections/Translation.tex
Proof in the appendix, fixed and added notes.

\hl{Furthermore, we introduce \textbf{@ObjWeak}, which is only an annotation for illustrating the translation, hence is not implemented in Lombok. By this, the real translation is divided into two parts: \textbf{@Obj} automatically refines the return types only, and \textbf{@ObjWeak} generates the constructor method $\QM{of}$. In the source code, the only annotation \textbf{@Obj} combines both of the work and finishes the translation at a time.}

\subsection{Translation Function}

\noindent$\begin{array}{l}
\InTextDef{18em}{[\![\mixinAnn\ \QM{interface}\ \C_0\ \QM{extends}\ \Cs\ \oC \methods\ \cC ]\!]
}{
\weakAnn\ \QM{interface}\ \C_0\ \QM{extends}\ \Cs\ \oC
\methods\ \methods' \cC
}\\
\InTextWith{\methods'=\otherMethod(\C_0,\methods)}
\end{array}$

\hl{To translate an interface annotated by \mixin, we add some other methods for type refinement, then add a new annotation \textbf{@ObjWeak} to the interface.}

\noindent$\begin{array}{l}
\InTextDef{18em}{[\![\weakAnn\ \QM{interface}\ \C_0\ \QM{extends}\ \Cs\ \oC \methods\ \cC ]\!]
}{
\emptyset\ \QM{interface}\ \C_0\ \QM{extends}\ \Cs\ \oC
\methods\ \method' \cC
}\\
\InTextWith{\valid(\C_0),\QM{of}\notin\dom(\methods) \mbox{ and } \method'=\ofMethod(\C_0)}
\end{array}$

\hl{To translate an interface annotated by \textbf{@ObjWeak}, we add the $\QM{of}$ method.}
However, first of all we check if the interface is valid for annotation:

\noindent$\valid(\C_0)$  holds if $\forall \m\in\dom(\C_0),$ if $\mh\QM; = \mBody(\m, \C_0),$ one case is satisfied:
$\isField(\method)$,
$\isWith(\method, \C_0)$
or
$\isSetter(\method,\C_0)$. \
%$\isClone(\method, \C_0)$.
That is, we can categorize all the \emph{not implemented} methods in a pattern that we know how to implement.

%To complete our formal definition we would need to add setters and \Q@with@.
Moreover, we check that the method \Q@of@ is not already defined by the user.
In our simplified formalization we consider this to be just an error.
In our prototype we keep overloading into account, and so we check that an \Q@of@ method with the same signature of the one we would generate is not already present.\marco{Do we check it?}\haoyuan{Not sure if it is $\QM{of}\notin\dom(\methods)$ or $\QM{of}\notin\dom(\C_0)$. It is an error if a static method overrides an instance method.}

@@

\haoyuan{I think $\QM{with#}\m\notin\dom(\methods)$ is not enough. The withM method with return type $I_0$ can also be defined already in a super interface. Like:
\[\begin{array}{l}\QM{
interface A}\ \oC\QM{int x(); B withX(int x);}\cC\\
\mixinAnn\ \QM{interface B extends A}\ \oC\cC\end{array}\]}

\noindent$\begin{array}{ll}
\InTextDef{20em}{\C_0\ \QM{with#}\m\oR \C\ \QM{_val}\cR\QM;\in
\otherMethod(\C_0,\methods)}{
 \isWith(\mBody(\QM{with#}\m, \C_0), \C_0)}\\
\InTextWith{\C\ \m\QM{();}\in \fieldsFunc(\C_0)
\mbox{ and } \QM{with#}\m\notin\dom(\methods)}\\
\InTextDef{20em}{\C_0\ \QM_\m\oR \C\ \QM{_val}\cR\QM;\in
\otherMethod(\C_0,\methods)}{\isSetter(\mBody(\QM_\m, \C_0), \C_0)}\\
\InTextWith{
\C\ \m\QM{();}\in \fieldsFunc(\C_0)
\mbox{ and } \QM_\m\notin\dom(\methods)}\\
\end{array}$

@@

\marco{ insert somewhere description of  fluent setter~\cite{the-lombock-thread-something-about-fluent-stuff}.
This allows for convenient and chains of setters, as we will show later \marco{insert forward reference when available}}.

\subsection{Results}
Informally, in a type correct interface table, if we translate a specific interface, then
the resulting table is type correct, or there is a subtype of the translated interface in the original table.
\textbf{THEOREM. }
For a given $\II_0\ldots\II_n$ interface table such that
$\forall\II\in\II_0\ldots\II_n, \II$ OK,\\*
if $\II_0$ has \mixin,
$\valid(\C_0)$  and $\QM{of}\notin\dom(\C_0)$,
there is no $\C<:\C_0$, there is no \Q@new @$\C_0$\Q@(){..}@,
then in the interface table
$[\![\II_0]\!]\II_1\ldots\II_n$\\*
$\forall\II\in[\![\II_0]\!]\II_1\ldots\II_n$ $\II$ OK.

To understand this theorem statement, we need to understand three kind of guarantees that we can offer for safety:
\begin{itemize}
\item \textit{Self coherence}: the generated code itself is well-typed; type errors are not present in code the user have not wrote.
In our case it means that either \mixin{} produces in controlled way an understandable error, or the class can be successfully annotate and the generated code is well typed.
We guarantee \textit{Self coherence}.

@@

\item \textit{Heir coherence}: Interfaces (and in general classes) inheriting from instrumented code are well typed if they was well typed without the instrumentation.
This would require to not add any (default or abstract) method to the annotated interfaces, including type refinement.
We do not guarantee \textit{Heir coherence}.
Indeed consider the following example

@@

By the translation rule, \mixin would  generate in \Q@B@  a method ``\Q@B withX(int x);@''.
This would break \Q@C@.

\end{itemize}
%The first two levels of safety are essential to our lightweight framework, nevertheless, the third one is not needed. In Java it implies not touching the annotated interface, and surely an alternative approach is to create a new interface and generate what we need. But since we are using Lombok for the translation, the transformation is applied to the annotated interface itself. But heir coherence is indeed an issue. See below how this is affected by our approach:

>>>>

We chose to modularly divide our translation in two parts, so that we can discuss about formal properties of those parts later. To this aim we introduce the annotation \Q:@ObjWeak:. Its role is only in the translation process, hence is not part of the classless java language.
\Q:@ObjWeak: generates the constructor method $\QM{of}$, while 
\mixin automatically refines the return types and calls \Q:@ObjWeak:.

\noindent$\begin{array}{l}
\InTextDef{16em}{[\![\mixinAnn\ \QM{interface}\ \C_0\ \QM{extends}\ \Cs\ \oC \methods\ \cC ]\!]
}{
[\![\weakAnn\ \QM{interface}\ \C_0\ \QM{extends}\ \Cs\ \oC
\methods\ \methods' \cC
]\!]}\\
\InTextWith{\methods'=\otherMethod(\C_0,\methods)}\\

\InTextDef{18em}{[\![\weakAnn\ \QM{interface}\ \C_0\ \QM{extends}\ \Cs\ \oC \methods\ \cC ]\!]
}{
\QM{interface}\ \C_0\ \QM{extends}\ \Cs\ \oC
\methods\ \ofMethod(\C_0) \cC
}\\
\InTextWith{\valid(\C_0),\QM{of}\notin\dom(\C_0) }
\end{array}$

As you see, we explicitly check if the interface is valid for annotation:

\noindent$\valid(\C_0)$  holds if $\forall \m\in\dom(\C_0),$ if $\mh\QM; = \mBody(\m, \C_0),$ one case is satisfied:
$\isField(\method)$,
$\isWith(\method, \C_0)$
or
$\isSetter(\method,\C_0)$. \
%$\isClone(\method, \C_0)$.

That is, we can categorize all the \emph{not implemented} methods in a pattern that we know how to implement.
Moreover, we check that the method \Q@of@ is not already defined by the user.
In our simplified formalization we consider this to be just an error.
In our prototype we keep overloading into account, and so we check that an \Q@of@ method with the same signature of the one we would generate is not already present.

@@

\haoyuan{I think $\QM{with#}\m\notin\dom(\methods)$ is not enough. The withM method with return type $I_0$ can also be defined already in a super interface. Like:
\[\begin{array}{l}\QM{
interface A}\ \oC\QM{int x(); B withX(int x);}\cC\\
\mixinAnn\ \QM{interface B extends A}\ \oC\cC\end{array}\]}
\marco{It is ok, in that case we just regenerate it identical}

\noindent$\begin{array}{ll}
\InTextDef{20em}{\C_0\ \QM{with#}\m\oR \C\ \QM{_val}\cR\QM;\in
\otherMethod(\C_0,\methods)}{
 \isWith(\mBody(\QM{with#}\m, \C_0), \C_0),}\\
\tab\tab{\C\ \m\QM{();}\in \fieldsFunc(\C_0)
\mbox{ and } \QM{with#}\m\notin\dom(\methods)}\\
\InTextDef{20em}{\C_0\ \QM_\m\oR \C\ \QM{_val}\cR\QM;\in
\otherMethod(\C_0,\methods)}{\isSetter(\mBody(\QM_\m, \C_0), \C_0),}\\
\tab\tab{
\C\ \m\QM{();}\in \fieldsFunc(\C_0)
\mbox{ and } \QM_\m\notin\dom(\methods)}\\
\end{array}$

@@

\subsection{Guaratees}
Now we try to understand what is the meaning of saying that our approach is correct, and more in genera, what it means to say that a Language tuning is correct.
We identify three types of guarancees: 
\begin{itemize}
\item \textit{Self coherence}: the generated code itself is well-typed; type errors are not present in code the user have not wrote.
In our case it means that either \mixin{} produces in controlled way an understandable error, or the class can be successfully annotate and the generated code is well typed.
We guarantee \textit{Self coherence}.

@@

\item \textit{Heir coherence}: Interfaces (and in general classes) inheriting from instrumented code are well typed if they was well typed without the instrumentation.
This would require to not add any (default or abstract) method to the annotated interfaces, including type refinement.
\mixin  do not guarantee \textit{Heir coherence}.
Indeed consider the following example

@@

By the translation rule, \mixin would  generate in \Q@B@  a method ``\Q@B withX(int x);@''.
This would break \Q@C@.
\end{itemize}
\subsection{Results}
Informally, in a type correct interface table, if we translate a specific interface, then
the resulting table is type correct, or there is a subtype of the translated interface in the original table.
\textbf{THEOREM. }
For a given $\II_0\ldots\II_n$ interface table such that
$\forall\II\in\II_0\ldots\II_n, \II$ OK,\\*
if $\II_0$ has \mixin,
$\valid(\C_0)$  and $\QM{of}\notin\dom(\C_0)$,
there is no $\C<:\C_0$, there is no \Q@new @$\C_0$\Q@(){..}@,
then in the interface table
$[\![\II_0]\!]\II_1\ldots\II_n$\\*
$\forall\II\in[\![\II_0]\!]\II_1\ldots\II_n$ $\II$ OK.

%The first two levels of safety are essential to our lightweight framework, nevertheless, the third one is not needed. In Java it implies not touching the annotated interface, and surely an alternative approach is to create a new interface and generate what we need. But since we are using Lombok for the translation, the transformation is applied to the annotated interface itself. But heir coherence is indeed an issue. See below how this is affected by our approach:
